---
title: "Aides Tests"
author: "Dr K"
date: "May 24, 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
require(tigerstats)
require(dplyr)
Scarolina<-read.csv(file="south_carolina_aides.csv",header=TRUE)
korea<-read.csv(file="korea_aides.csv",header=TRUE)
cenAfrica<-read.csv(file="central_africa_aides.csv",header=TRUE)
```

#Instructions

Three new preventative aides drugs were tested in clinical trials in 2015. The trial designs were modeled after the famous RV_144 Aides Trials in Tailand in 2009.  Analyze and report on the apparent effectiveness of the three different drugs. Does sex of the participant seem to be a factor for any of the drugs?

#Methods 

This Aides study is similar to the famous RV_144 Aides Trial in Thailand in 2009. The project is to analyze the three drugs for South Carolina, Korea and Central Africa being tested among female and male trial candidates. We will test the effect of the drugs on the individual sexes females and males, as well as both sexes together.
Furthermore, we will use tigerstats and dplr to obtain barcharts,numerical results, inferential results by running quisquare test. 
In the end we want to know if the sex of the participant has a correlation with the effects of the drugs. 

#Results

#Graphical Results

# South carolina 

We will subset the data by sex to see if the drug is sex specific.


```{r}
results<- xtabs(~infected + group, data =  Scarolina)
barchartGC(results, type = "percent")
```

Based on the barchart above, the results indicate that the placebo and the drug both have about the same effect on both sex groups. There is about a 50%-50% effect from the drug and also about the same 50%-50% effect from the placebo. 

```{r}
scmales<- filter(Scarolina, sex == "M")
resultsM<- result<- xtabs(~infected + group, data = scmales)
barchartGC(resultsM, type = "percent")
```
The barchart above pulled out the percent of those infected and the non-infected males. Based on the results above the drug is not effecteive on males becasue more than 55% got aids on the drug and about 45% on the placebo got aids. The percent of the males who didn't get aids on the placebo was about 50% and those who got aids on the drug was about 49%. 

```{r}
scfemales<- filter(Scarolina, sex == "F")
resultsF<- result<- xtabs(~infected + group, data = scfemales)
barchartGC(resultsF, type = "percent")

```

Based on the barchart above the drug works on the females because less than 40% got aids on the drug and more than 60% got aids on the placebo. About 50% of those on the drug din't get aids and about 49% on the placebo didn't get aids. 

# Central Africa

We will subset the data by sex to see if the drug is sex specific.

```{r}
results<- xtabs(~infected + group, data =  cenAfrica)
barchartGC(results, type = "percent")
```

Based on the barchart above, the data shows that about 47% of both sex groups got aids on the drug. More than 50% on the placebo got aids.Thus, the drug was about 47% effective on both sex groups. And about 50% on the drug and placebo didn't get aids. 

```{r}
cAmales<- filter(cenAfrica, sex == "M")
resultsM<- result<- xtabs(~infected + group, data = cAmales)
barchartGC(resultsM, type = "percent")
```

Based on the data represented above, slightly less than 50% of the drug was effective on males. The placebo was about 51% effective and of those who didn't get aids was 50%-50% for both on the drug and on the placebo.  

```{r}
cAfemales<- filter(cenAfrica, sex == "F")
resultsF<- result<- xtabs(~infected + group, data = cAfemales)
barchartGC(resultsF, type = "percent")
```

Based on the data represented above, the drug was 46% effective on females. 55% of those who took the placebo got aids and of those who didn't get aids was 50%-50% for both on the drug and on the placebo. Therefore the drug kinda worked. 

# Korea

We will subset the data by sex to see if the drug is sex specific.

```{r}
results<- xtabs(~infected + group, data =  korea)
barchartGC(results, type = "percent")
```

Based on the data provided above, the drug was about 45% effective on the Koreans. The data indicates that 45% got aids and 56% on the placebo got aids. And of those who didn't get aids on the drug and the placebo were about 50%- 50%. 

```{r}
KoreaMales<- filter(korea, sex == "M")
resultsM<- result<- xtabs(~infected + group, data = KoreaMales)
barchartGC(resultsM, type = "percent")
```

Based on the data above, about 36% of those who took the drug got aids and more than 65% on the placebo got aids. In the group with no aids the percent shows about the same for thsoe on the drug and those who took the placebo, 50%-50%. Thus, the data indicates that the drug works on the Korean males. 

```{r}
KoreaFemales<- filter(korea, sex == "F")
resultsF<- result<- xtabs(~infected + group, data = KoreaFemales)
barchartGC(resultsF, type = "percent")
```


The data above shows that the females who took the drug got about 65% aids. And those on the placebo got about 37% aids. And of the females who didn't get aids was about 50%-50% for those who were on the placebo and on the drug. Based on this data, the drug didn't work on the females.  

#Numerical Results

```{r}
chisqtestGC(~infected + group, data = Scarolina)
```

 The null hypothesis is independent because both the placebo group and the Scarolina drug group counted for the same number 119.5. However, the observed count shows that 118 on the drug got aids and 121 on the placebo got aids. 

```{r}
chisqtestGC(~infected + group, data = cenAfrica)
```

The CenAfrica drug is independent becasue the observed results show that 101 of the group who took the drug was infected and 110 on the placebo were not infected. The null hypothesis reads that both the drug group and the placebo group were infected by 105.5 count.  

```{r}
chisqtestGC(~infected + group, data = korea)
```

The null hypothesis is independent from the observed count because the Korea group on the drug got aids by 103 count and those on the placebo were infected by 131 count. Based on our observations, the drug worked. 

```{r}
chisqtestGC(results, graph = TRUE)
```

#Inferential Results

```{r}
rowPerc(results)
```

The row percent shows that out of 100, the group who took the drug got aids by 44% and thsoe on the placebo got aids by 56%. The participants who didn't get aids was about 50%.

```{r}
rowPerc(resultsM)
```

From the male percent row, 33% of the drug group got aids and 67% on the placebo got aids. 
Of thsoe who didn't get aids on the drug and the placebo was roughly about 50%. 

```{r}
rowPerc(resultsF)
```

From the female row percent, 65% on the drug got aids and 35% on the placebo got aids. Of those who didn't get aids, about 49.5% were in the count. 

# Conclusion

In conclusion, the graphical results show that the Korea drug is more effective than the other two drug by about 45%. The drug was more effective on the males than the females by  36%-64%. 
In comparison to the SCaroliona results, the drug was only effective by about 50%. The drug was efefctive different between the males and the females group based on the resutls which show 58%- 40%. So, the drug was more effective on the females. 
Based on the resutls on the CenAfrica results, the drug was only about 47% effective. And between the males and females group, the drug was 50%-47% effective. 

I would recommend the Korean drug to a male more than the other two drugs. And we can see more or less the difference of the efefct of the drug based on the sex. 


